\thetitle

### 2023-06-03 lang-design.tex
Fix typo.

These four equations uniquely describe the "tm_prect_STLC" on the four constructors and thus "tm_prect_STLC" cannot be a trivial function. This partial recursor also corresponds to the dependent eliminator for the non-extensible version of "tm".

@@

We emphasize that in \cref{thm:prec-complete}, each function $"d"_i$ can
actually be considered as a constructor, because they can be reflected
to real constructors of "C" using the left inverse "linv". Thus, \cref{thm:prec-complete}
implies that (1) every future extension of the inductive type can
support this partial recursion (trivially); (2) every type supporting
this partial recursor with its computational axioms at least supports
these constructors because of the embedding. In other words, \textit{a
type (at least) supports these constructors if and only if this type
supports the corresponding partial recursor (with the computational
axioms)}.  Thus, we can argue that the partial recursor gives a sound and
complete extensional characterization of all the extension of a given (non-indexed)
inductive type.\YZ{What about indexed inductive types?}\EDJreply{Done. I also have a formalization of this proof now, for indexed type and dependent eliminator. Though the formalization is about single constructor.}

>>>>

"tm_prect_STLC" cannot be a trivial function even though its return type has "option". Because these four equations uniquely describe the "tm_prect_STLC" on the four constructors and make "tm_prect_STLC" behave similar to the ordinary dependent eliminator of the non-extensible version of "tm".

@@

We emphasize that in \cref{thm:prec-complete}, each function $"d"_i$ can
actually be considered as a constructor, because they can be reflected
to real constructors of "C" using the left inverse "linv". Thus, \cref{thm:prec-complete}
implies that (1) every future extension of the inductive type can
support this partial recursion (trivially); (2) every type supporting
this partial recursor with its computational axioms at least supports
these constructors because of the embedding. In other words, \textit{a
type (at least) supports these constructors if and only if this type
supports the corresponding partial recursor (with the computational
axioms)}.  Thus, we can argue that the partial recursor gives a sound and
complete extensional characterization of all the extensions of a given (non-indexed)
inductive type.\YZ{What about indexed inductive types?}\EDJreply{Done. I also have a formalization of this proof now, for indexed type and dependent eliminator. Though the formalization is about single constructor.}

### 2023-06-03 metatheory2.tex
Fix typo.

\noindentparagraph{MLTT as a programming language.}  Conventionally, the operational semantic sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantic in our MLTT. It is no doubt that MLTT is a logical system where we can write proofs, but it is unclear if MLTT can really be considered as a programming language.

@@

Once it is clear that the syntax of our MLTT as a logic system is a quotiented 
data, then it is natural to consider model of this logic system 
as a function mapping from those quotiented data (syntax). The (semantic) model introduced below 
will follow this idea. More specifically, the semantic model as a function will have to respects 
judgemental equalities to be a well-defined function from quotiented data. In other words,
for two judgementally equal syntax pieces, the model needs to map them into the same data.

>>>>

\noindentparagraph{MLTT as a programming language.}  Conventionally, the operational semantics sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantics in our MLTT. It is no doubt that MLTT is a logical system where we can write proofs, but it is unclear if MLTT can really be considered as a programming language.

@@

Once it is clear that the syntax of our MLTT as a logic system is a quotiented 
data, then it is natural to consider model of this logic system 
as a function mapping from those quotiented data (syntax). The (semantic) model introduced below 
will follow this idea. More specifically, the semantic model as a function will have to respect 
judgemental equalities to be a well-defined function from quotiented data. In other words,
for two judgementally equal syntax pieces, the model needs to map them into the same data.

### 2023-06-03 ttintro.tex
Fix typo.

\noindentparagraph{\TT as a programming language.}  Conventionally, the operational semantic sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantic in our \TT and doubt if \TT can really be considered as a programming language.

>>>>

\noindentparagraph{\TT as a programming language.}  Conventionally, the operational semantics sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantics in our \TT and doubt if \TT can really be considered as a programming language.
